---
title: "Primary Analysis"
author: "Christian Wollmann"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
    toc_depth: 2
    theme: united
---

0. Reading in required packages
```{r}
library(tidyverse) 
library(car)
library(DT)
library(dplyr)
library(tidyr)
library(lme4)
library(ggplot2)
library(influence.ME)
library(patchwork)
library(performance)
library(nortest)
library(parameters)
library(emmeans)
library(boot)
library(r2glmm)
library(clubSandwich)
```

1. Model Specification

1.1 Reading in Data
```{r}
df_primary <- read.csv("df_long.csv")


df_primary$val_cat <- factor(df_primary$val_cat, levels = c("neg", "neu", "pos"))
df_primary$gr <- factor(df_primary$gr, levels = c("20Hz_online_exp", "20Hz_online_sham"))
```

1.2 Specification of lme4-models
```{r}
p1 <- lmer(mem ~ gr * val_cat + (1|subj), data = df_primary)

p2 <- lmer(mem ~ gr * val_cat + age + sex + (1|subj), data = df_primary)

p3 <- lmer(mem ~ gr * val_cat + age + sex + rMT + (1|subj), data = df_primary)
```

1.3 Distribution of DV
```{r}
m <- ggplot(df_primary, aes(x = val_cat, y = mem, fill = gr)) +
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(width = 1), 
               alpha = 0.5, color = "black") +
  stat_summary(fun.data = mean_cl_normal, 
               geom = "errorbar", 
               position = position_dodge(width = 1), 
               width = 0.2, color = "black") +
  scale_fill_manual(values = c("20Hz_online_exp" = "#0072B2",
                               "20Hz_online_sham" = "#D55E00"),
                    labels = c("experimental", "control"),
                    name = "Group") +
  scale_x_discrete(labels = c("neg" = "negative", 
                              "neu" = "neutral", 
                              "pos" = "positive")) +
  labs(x = "", y = "", fill = "") +
  theme_minimal() +
  theme(legend.title = element_text(hjust = 0.5)) 

m
```

2. Verifying assumptions

2.1 Univariate outliers

visualization
```{r}
g1 <- ggplot(df_primary, aes(x = "", y = mem)) +  
  stat_boxplot(geom = "errorbar", width = 0.6, color = "black", alpha = 0.5, linewidth = 0.3) +
  geom_boxplot(fill = "grey", color = "black", alpha = 0.5, linewidth = 0.3, outlier.size = 2, outlier.shape = 8) +  
  geom_jitter(aes(color = gr), width = 0.3, height = 0, alpha = 0.8) +  
  scale_color_manual(
    values = c("20Hz_online_exp" = "#0072B2", 
               "20Hz_online_sham" = "#D55E00"),
    labels = c("experimental", "control"),
    name = "Group"
  ) +
  scale_y_continuous(limits = c(0, 15)) +
  labs(
    x = NULL,  # entfernt x-Achsentitel
    y = NULL,  # entfernt y-Achsentitel
    title = NULL
  ) +
  theme_minimal() +
  theme(
    axis.text.y = element_text(size = 10),
    legend.title = element_text(size = 10, hjust = 0.5),
    legend.text = element_text(size = 9),
    panel.grid.minor = element_blank(), 
    panel.grid.major.x = element_blank(),
    axis.line = element_line(color = "black", linewidth = 0.5)
  )

g1
```

quantification
```{r}
Q1 <- quantile(df_primary$mem, 0.25, na.rm = TRUE)
Q3 <- quantile(df_primary$mem, 0.75, na.rm = TRUE)
IQR_value <- IQR(df_primary$mem, na.rm = TRUE)

lower_bound <- Q1 - 1.5 * IQR_value
upper_bound <- Q3 + 1.5 * IQR_value

outliers <- df_primary %>%
  filter(mem < lower_bound | mem > upper_bound)

outliers
```

2.2 Multivariate Outliers: Cooks Distance

quantification
```{r}
#cd based on influential cases
inf_p1 <- influence(p1, obs = TRUE)
inf_p2 <- influence(p2, obs = TRUE)
inf_p3 <- influence(p3, obs = TRUE)

cd_p1 <- cooks.distance(inf_p1)
cd_p2 <- cooks.distance(inf_p2)
cd_p3 <- cooks.distance(inf_p3)

#find observations exceeding thresholds
critical_threshold <- 1
conservative_threshold <- 4 / nrow(df_primary)

analyze_cooks_distance <- function(cd, model_name) {
  critical_points <- which(cd > critical_threshold)
    conservative_points <- which(cd > conservative_threshold)
  cat(paste("\n--- Cook's Distance Analysis for", model_name, "---\n"))
  
  if (length(critical_points) > 0) {
    cat("Indizes (CD > 1):\n")
    print(critical_points)
  } else {
    cat("Keine Punkte mit CD > 1 gefunden.\n")
  }

  if (length(conservative_points) > 0) {
    cat("Indizes (CD > 4/N):\n")
    print(conservative_points)
  } else {
    cat("Keine Punkte mit CD > 4/N gefunden.\n")
  }
}

analyze_cooks_distance(cd_p1, "p1")
analyze_cooks_distance(cd_p2, "p2")
analyze_cooks_distance(cd_p3, "p3")

#mapping observations and subject
cd4n_p1 <- c(3, 19, 24)
cd4n_p2 <- c(3, 24)
cd4n_p3 <- c(3, 24)

subj_cd4n_p1 <- df_primary$subj[cd4n_p1]
subj_cd4n_p2 <- df_primary$subj[cd4n_p2]
subj_cd4n_p3 <- df_primary$subj[cd4n_p3]

cat("\n--- Cook's Distance > 4/N: h1 ---\n")
cat("subj IDs:", subj_cd4n_p1, "\n")

cat("\n--- Cook's Distance > 4/N: h2 ---\n")
cat("subj IDs:", subj_cd4n_p2, "\n")

cat("\n--- Cook's Distance > 4/N: h3 ---\n")
cat("subj IDs:", subj_cd4n_p3, "\n")
```

visualization
```{r}
y_threshold <- 4/nrow(df_primary)
y_limit <- range(c(cd_p1, cd_p2, cd_p3, y_threshold), na.rm = TRUE)

par(mfrow = c(1, 3), mai = c(0.5, 0.6, 0.3, 0.25), oma = c(3, 0, 0, 0))

#H1
plot(cd_p1, type = "h", main = "", 
     ylab = "", xlab = "", ylim = y_limit, cex.lab = 1.2, col = "black")
abline(h = 1, col = "#0072B2", lty = 2)
abline(h = y_threshold, col = "#CC79A7", lty = 2)
segments(x0 = cd4n_p1, y0 = 0, x1 = cd4n_p1, y1 = cd_p1[cd4n_p1], col = "red", lwd = 1)

#H2
plot(cd_p2, type = "h", main = "", 
     ylab = "", xlab = "", ylim = y_limit, cex.lab = 1.2, col = "black")
abline(h = 1, col = "#0072B2", lty = 2)
abline(h = y_threshold, col = "#CC79A7", lty = 2)
segments(x0 = cd4n_p2, y0 = 0, x1 = cd4n_p2, y1 = cd_p2[cd4n_p2], col = "red", lwd = 1)

#H3
plot(cd_p3, type = "h", main = "", 
     ylab = "", xlab = "", ylim = y_limit, cex.lab = 1.2, col = "black")
abline(h = 1, col = "#0072B2", lty = 2)
abline(h = y_threshold, col = "#CC79A7", lty = 2)
segments(x0 = cd4n_p3, y0 = 0, x1 = cd4n_p3, y1 = cd_p3[cd4n_p3], col = "red", lwd = 1)

mtext("Observation Index", side = 1, line = 1.5, outer = TRUE, cex = par("cex.lab"))

par(mfrow = c(1, 1))
```

looking at subject variable combinations in raw dataset
```{r}
unique_subjects <- unique(c(subj_cd4n_p1, subj_cd4n_p2, subj_cd4n_p3))

unique_subjects <- sort(unique_subjects)
unique_subjects
df_20hz %>% filter(VP_nr %in% c(206 ,212, 213))
```

exclusion of subject 212
```{r}
df_primary <- df_primary %>% filter(subj != 212) 
```

respecification of models
```{r}
p1 <- lmer(mem ~ gr * val_cat + (1|subj), data = df_primary)

p2 <- lmer(mem ~ gr * val_cat + age + sex + (1|subj), data = df_primary)

p3 <- lmer(mem ~ gr * val_cat + age + sex + rMT + (1|subj), data = df_primary)
```

calculating new descriptives for primary analysis
```{r}

n_subjects_per_group <- df_primary %>%
  group_by(gr) %>%
  summarise(n_probanden = n_distinct(subj), .groups = "drop")

sex_distribution <- df_primary %>%
  group_by(gr, sex) %>%
  summarise(n = n_distinct(subj), .groups = "drop") %>%
  arrange(gr, sex)

subject_level_age <- df_primary %>%
  group_by(subj, gr) %>%
  summarise(age = first(age), .groups = "drop")

age_summary <- subject_level_age %>%
  group_by(gr) %>%
  summarise(
    mean_age = mean(age, na.rm = TRUE),
    sd_age = sd(age, na.rm = TRUE),
    .groups = "drop"
  )

wilcox_age <- wilcox.test(age ~ gr, data = subject_level_age)

subject_level_rMT <- df_primary %>%
  group_by(subj, gr) %>%
  summarise(rMT = first(rMT), .groups = "drop")

rMT_summary <- subject_level_rMT %>%
  group_by(gr) %>%
  summarise(
    mean_rMT = mean(rMT, na.rm = TRUE),
    sd_rMT = sd(rMT, na.rm = TRUE),
    .groups = "drop"
  )

wilcox_rMT <- wilcox.test(rMT ~ gr, data = subject_level_rMT)

mem_summary_val_cat <- df_primary %>%
  group_by(gr, val_cat) %>%
  summarise(
    mean_mem = mean(mem, na.rm = TRUE),
    sd_mem = sd(mem, na.rm = TRUE),
    .groups = "drop"
  )

df_split_val_cat <- df_primary %>%
  group_split(val_cat)

wilcox_results_val_cat <- lapply(df_split_val_cat, function(data_piece) {
  wilcox.test(mem ~ gr, data = data_piece)
})

names(wilcox_results_val_cat) <- df_primary %>%
  distinct(val_cat) %>%
  pull(val_cat)

subject_sums <- df_primary %>%
  group_by(gr, subj) %>%
  summarise(
    mem_sum = sum(mem, na.rm = TRUE),
    .groups = "drop"
  )

aggregated_summary <- subject_sums %>%
  group_by(gr) %>%
  summarise(
    mean_aggregated_mem = mean(mem_sum, na.rm = TRUE),
    sd_aggregated_mem = sd(mem_sum, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  )

wilcox_test_aggregated <- wilcox.test(mem_sum ~ gr, data = subject_sums)

n_subjects_per_group
sex_distribution
age_summary
wilcox_age
rMT_summary
wilcox_rMT
mem_summary_val_cat
wilcox_results_val_cat
aggregated_summary
wilcox_test_aggregated
```

2.3 Multicollinearity
quantification: VIF
```{r}
check_collinearity(p1)
check_collinearity(p2)
check_collinearity(p3)
```

2.4 Normal distribution of errors
calculate standardized residuals
```{r}
df_primary$residuals_p1 <- resid(p1)
df_primary$residuals_p2 <- resid(p2)
df_primary$residuals_p3 <- resid(p3)

df_primary$stand_resid_p1 <- scale(df_primary$residuals_p1)[, 1]
df_primary$stand_resid_p2 <- scale(df_primary$residuals_p2)[, 1]
df_primary$stand_resid_p3 <- scale(df_primary$residuals_p3)[, 1]
```

preparing density distribution and KDE for plotting
```{r}
# KDE
p1_density <- data.frame(
  x = density(df_primary$stand_resid_p1)$x,
  y = density(df_primary$stand_resid_p1)$y,
  type = "Empirical Density"
)

p2_density <- data.frame(
  x = density(df_primary$stand_resid_p2)$x,
  y = density(df_primary$stand_resid_p2)$y,
  type = "Empirical Density"
)

p3_density <- data.frame(
  x = density(df_primary$stand_resid_p3)$x,
  y = density(df_primary$stand_resid_p3)$y,
  type = "Empirical Density"
)

#normal distribution
p1_normal <- data.frame(
  x = seq(min(df_primary$stand_resid_p1), max(df_primary$stand_resid_p1), length.out = 100),
  y = dnorm(seq(min(df_primary$stand_resid_p1), max(df_primary$stand_resid_p1), length.out = 100)),
  type = "Normal Distribution"
)

p2_normal <- data.frame(
  x = seq(min(df_primary$stand_resid_p2), max(df_primary$stand_resid_p2), length.out = 100),
  y = dnorm(seq(min(df_primary$stand_resid_p2), max(df_primary$stand_resid_p2), length.out = 100)),
  type = "Normal Distribution"
)

p3_normal <- data.frame(
  x = seq(min(df_primary$stand_resid_p3), max(df_primary$stand_resid_p3), length.out = 100),
  y = dnorm(seq(min(df_primary$stand_resid_p3), max(df_primary$stand_resid_p3), length.out = 100)),
  type = "Normal Distribution"
)
```

Visualization
```{r}
#P1
p1_lines <- rbind(p1_density, p1_normal)

p1_hist <- ggplot(df_primary, aes(x = stand_resid_p1)) +
  geom_histogram(aes(y = ..density..), fill = "grey", color = "#000000", binwidth = 0.25) +
  geom_line(data = p1_lines, aes(x = x, y = y, color = type), linewidth = 1) +
  scale_color_manual(name = "Line Type", 
                     values = c("Empirical Density" = "#CC79A7", 
                                "Normal Distribution" = "#F0E442")) +
  labs(title = "", x = "", y = "") +
  theme_minimal() +
  theme(legend.title = element_text(hjust = 0.5)) 

p1_hist

df_primary$theoretical_quantiles_p1 <- qqnorm(df_primary$stand_resid_p1, plot.it = FALSE)$x

p1_qq <- ggplot(df_primary, aes(x = theoretical_quantiles_p1, y = stand_resid_p1, color = gr)) +
  geom_jitter(width = 0.3, height = 0, size = 1.5, alpha = 0.7) +
  geom_abline(intercept = mean(df_primary$stand_resid_p1), slope = sd(df_primary$stand_resid_p1), color = "#CC79A7", linewidth = 1) +
  scale_color_manual(
    values = c("20Hz_online_exp" = "#0072B2", 
               "20Hz_online_sham" = "#D55E00"),
    labels = c("experimental", "control"),
    name = "Group"
  ) +
  labs(title = "", x = "", y = "") +
  theme_minimal() +
   theme(legend.title = element_text(hjust = 0.5)) 

p1_qq

#P2
p2_lines <- rbind(p2_density, p2_normal)

p2_hist <- ggplot(df_primary, aes(x = stand_resid_p2)) +
  geom_histogram(aes(y = ..density..), fill = "grey", color = "#000000", binwidth = 0.25) +
  geom_line(data = p2_lines, aes(x = x, y = y, color = type), linewidth = 1) +
  scale_color_manual(name = "Line Type", 
                     values = c("Empirical Density" = "#CC79A7", 
                                "Normal Distribution" = "#F0E442")) +
  labs(title = "", x = "", y = "") +
  theme_minimal() +
   theme(legend.title = element_text(hjust = 0.5)) 
p2_hist

df_primary$theoretical_quantiles_p2 <- qqnorm(df_primary$stand_resid_p2, plot.it = FALSE)$x

p2_qq <- ggplot(df_primary, aes(x = theoretical_quantiles_p2, y = stand_resid_p2, color = gr)) +
  geom_jitter(width = 0.3, height = 0, size = 1.5, alpha = 0.7) +
  geom_abline(intercept = mean(df_primary$stand_resid_p2), slope = sd(df_primary$stand_resid_p2), color = "#CC79A7", linewidth = 1) +
scale_color_manual(
    values = c("20Hz_online_exp" = "#0072B2", 
               "20Hz_online_sham" = "#D55E00"),
    labels = c("experimental", "control"),
    name = "Group"
  ) +  labs(title = "", x = "", y = "") +
  theme_minimal() +
 theme(legend.title = element_text(hjust = 0.5)) 
p2_qq

#P3
p3_lines <- rbind(p3_density, p3_normal)

p3_hist <- ggplot(df_primary, aes(x = stand_resid_p3)) +
  geom_histogram(aes(y = ..density..), fill = "grey", color = "#000000", binwidth = 0.25) +
  geom_line(data = p3_lines, aes(x = x, y = y, color = type), linewidth = 1) +
  scale_color_manual(name = "Line Type", 
                     values = c("Empirical Density" = "#CC79A7", 
                                "Normal Distribution" = "#F0E442")) +
  labs(title = "", x = "", y = "") +
  theme_minimal() +
 theme(legend.title = element_text(hjust = 0.5)) 
p3_hist

df_primary$theoretical_quantiles_p3 <- qqnorm(df_primary$stand_resid_p3, plot.it = FALSE)$x

p3_qq <- ggplot(df_primary, aes(x = theoretical_quantiles_p3, y = stand_resid_p3, color = gr)) +
  geom_jitter(width = 0.3, height = 0, size = 1.5, alpha = 0.7) +
  geom_abline(intercept = mean(df_primary$stand_resid_p3), slope = sd(df_primary$stand_resid_p3), color = "#CC79A7", linewidth = 1) +
scale_color_manual(
    values = c("20Hz_online_exp" = "#0072B2", 
               "20Hz_online_sham" = "#D55E00"),
    labels = c("experimental", "control"),
    name = "Group"
  ) +  labs(title = "", x = "", y = "") +
  theme_minimal() +
 theme(legend.title = element_text(hjust = 0.5)) 
p3_qq
```

quantification
```{r}
#P1
shapiro_residuals_p1 <- shapiro.test(df_primary$residuals_p1)
ad_residuals_p1 <- ad.test(df_primary$residuals_p1)

cat("\n#---------------------------------------#\n")
cat("## Model p1 - Normality Tests\n")
cat("\nShapiro-Wilk Test:\n")
print(shapiro_residuals_p1)
cat("\nAnderson-Darling Test:\n")
print(ad_residuals_p1)

#P2
shapiro_residuals_p2 <- shapiro.test(df_primary$residuals_p2)
ad_residuals_p2 <- ad.test(df_primary$residuals_p2)

cat("\n#---------------------------------------#\n")
cat("## Model p2 - Normality Tests\n")
cat("\nShapiro-Wilk Test:\n")
print(shapiro_residuals_p2)
cat("\nAnderson-Darling Test:\n")
print(ad_residuals_p2)

#P3
shapiro_residuals_p3 <- shapiro.test(df_primary$residuals_p3)
ad_residuals_p3 <- ad.test(df_primary$residuals_p3)

cat("\n#---------------------------------------#\n")
cat("## Model p3 - Normality Tests\n")
cat("\nShapiro-Wilk Test:\n")
print(shapiro_residuals_p3)
cat("\nAnderson-Darling Test:\n")
print(ad_residuals_p3)
```

2.5 Variance homogeneity
visualization
```{r}
#P1
df_primary$fitted_p1 <- fitted(p1)

var_p1 <- ggplot(data = df_primary, aes(x = fitted_p1, y = residuals_p1, color = gr)) +
  geom_point(size = 2, alpha = 0.7) +
  geom_hline(aes(yintercept = 0, linetype = "No Deviation"), color = "black") +
  geom_smooth(method = "loess", aes(linetype = "Fitted Residuals"), color = "#CC79A7", se = FALSE, linewidth = 1) +
  scale_color_manual(
    values = c("20Hz_online_exp" = "#0072B2", "20Hz_online_sham" = "#D55E00"),
    name = "Group"
  ) +
  geom_segment(aes(xend = fitted_p1, yend = 0, linetype = "Residual Distance"), color = "#009E73", linewidth = 0.1) +
  scale_linetype_manual(
    values = c("No Deviation" = "dashed", "Fitted Residuals" = "solid", "Residual Distance" = "dashed"),
    name = "Line Type"
  ) +
  labs(title = "",
       x = "",
       y = "") +
  theme_minimal() +
 theme(legend.title = element_text(hjust = 0.5)) 
var_p1

#P2
df_primary$fitted_p2 <- fitted(p2)

var_p2 <- ggplot(data = df_primary, aes(x = fitted_p2, y = residuals_p2, color = gr)) +
  geom_point(size = 2, alpha = 0.7) +
  geom_hline(aes(yintercept = 0, linetype = "No Deviation"), color = "black") +
  geom_smooth(method = "loess", aes(linetype = "Fitted Residuals"), color = "#CC79A7", se = FALSE, linewidth = 1) +
  scale_color_manual(
    values = c("20Hz_online_exp" = "#0072B2", "20Hz_online_sham" = "#D55E00"),
    name = "Group"
  ) +
  geom_segment(aes(xend = fitted_p2, yend = 0, linetype = "Residual Distance"), color = "#009E73", linewidth = 0.1) +
  scale_linetype_manual(
    values = c("No Deviation" = "dashed", "Fitted Residuals" = "solid", "Residual Distance" = "dashed"),
    name = "Line Type"
  ) +
  labs(title = "",
       x = "",
       y = "") +
  theme_minimal() +
 theme(legend.title = element_text(hjust = 0.5)) 
var_p2

#P3
df_primary$fitted_p3 <- fitted(p3)

var_p3 <- ggplot(data = df_primary, aes(x = fitted_p3, y = residuals_p3, color = gr)) +
  geom_point(size = 2, alpha = 0.7) +
  geom_hline(aes(yintercept = 0, linetype = "No Deviation"), color = "black") +
  geom_smooth(method = "loess", aes(linetype = "Fitted Residuals"), color = "#CC79A7", se = FALSE, linewidth = 1) +
  scale_color_manual(
    values = c("20Hz_online_exp" = "#0072B2", "20Hz_online_sham" = "#D55E00"),
    name = "Group"
  ) +
  geom_segment(aes(xend = fitted_p3, yend = 0, linetype = "Residual Distance"), color = "#009E73", linewidth = 0.1) +
  scale_linetype_manual(
    values = c("No Deviation" = "dashed", "Fitted Residuals" = "solid", "Residual Distance" = "dashed"),
    name = "Line Type"
  ) +
  labs(title = "",
       x = "",
       y = "") +
  theme_minimal() +
 theme(legend.title = element_text(hjust = 0.5)) 
var_p3
```

quantification
```{r}
bp_p1 <- check_heteroscedasticity(p1)
bp_p2 <- check_heteroscedasticity(p2)
bp_p3 <- check_heteroscedasticity(p3)

print(bp_p1)
print(bp_p2)
print(bp_p3)
```

3. Inferential Analysis
3.1 Model Fit
```{r}
model_list <- list(p1, p2, p3)
model_names <- c("P1", "P2", "P3")

model_comparison <- data.frame(
  Model = model_names,
  AIC = sapply(model_list, AIC),
  BIC = sapply(model_list, BIC)
)

print(model_comparison)
```

3.2 Model Results P1
linear mixed model results
```{r}
p1 <- lmer(mem ~ gr * val_cat + (1|subj), data = df_primary)
summary(p1)
model_parameters(p1, ci = 0.95)
```

bootstrapped effect sizes
```{r}
boot_r2_function <- function(model) {
  r2beta(model, method = "nsj")$Rsq
}

set.seed(123)  
boot_p1_results <- bootMer(p1, FUN = boot_r2_function, nsim = 1000, use.u = TRUE, type = "parametric")

boot_r2_means <- apply(boot_p1_results$t, 2, mean)
boot_r2_cis <- apply(boot_p1_results$t, 2, quantile, probs = c(0.025, 0.975))

boot_p1_summary <- data.frame(
  Effect = r2beta(p1, method = "nsj")$Effect,
  Boot_R2 = round(boot_r2_means, 4),
  CI_Lower = round(boot_r2_cis[1, ], 4),
  CI_Upper = round(boot_r2_cis[2, ], 4)
)

print(boot_p1_summary)
```

interaction plot
```{r}
emm_p1 <- emmeans(p1, ~ gr * val_cat)
emm_df_p1 <- as.data.frame(emm_p1)

plot_p1 <- ggplot(emm_df_p1, aes(x = val_cat, y = emmean, color = gr, group = gr)) +
  geom_line(linewidth = 1, position = position_dodge(0.3)) +
  geom_point(size = 3, position = position_dodge(0.3)) +
  geom_errorbar(
    aes(ymin = lower.CL, ymax = upper.CL),
    width = 0.15,
    position = position_dodge(0.3)
  ) +
  scale_x_discrete(labels = c("neg" = "Negative", "neu" = "Neutral", "pos" = "Positive")) +
  scale_color_manual(
    values = c("20Hz_online_exp" = "#0072B2", "20Hz_online_sham" = "#D55E00"),
    labels = c("experimental", "control"),
               name = "Group") +
  labs(
    title = "",
    x = "",
    y = ""
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 11),
    legend.title = element_text(size = 12),
    legend.title.align = 0.5,
    legend.text = element_text(size = 10)
  )

print(plot_p1)
```

3.3 Model Results P2
linear mixed model results
```{r}
p2 <- lmer(mem ~ gr * val_cat + age + sex + (1|subj), data = df_primary)
summary(p2)
model_parameters(p2, ci = 0.95
```

bootstrapped effect sizes
```{r}
boot_r2_function <- function(model) {
  r2beta(model, method = "nsj")$Rsq
}

set.seed(123)
boot_p2_results <- bootMer(p2, FUN = boot_r2_function, nsim = 1000, use.u = TRUE, type = "parametric")

boot_r2_means_p2 <- apply(boot_p2_results$t, 2, mean)
boot_r2_cis_p2 <- apply(boot_p2_results$t, 2, quantile, probs = c(0.025, 0.975))

boot_p2_summary <- data.frame(
  Effect = r2beta(p2, method = "nsj")$Effect,
  Boot_R2 = round(boot_r2_means_p2, 4),
  CI_Lower = round(boot_r2_cis_p2[1, ], 4),
  CI_Upper = round(boot_r2_cis_p2[2, ], 4)
)

print(boot_p2_summary)
```

3.4 Model Results P3
linear mixed model results
```{r}
p3 <- lmer(mem ~ gr * val_cat + age + sex + rMT + (1|subj), data = df_primary)
summary(p2)
model_parameters(p2, ci = 0.95)
```

bootstrapped effect sizes
```{r}
boot_r2_function <- function(model) {
  r2beta(model, method = "nsj")$Rsq
}

set.seed(123)
boot_p3_results <- bootMer(p3, FUN = boot_r2_function, nsim = 1000, use.u = TRUE, type = "parametric")

boot_r2_means_p3 <- apply(boot_p3_results$t, 2, mean)
boot_r2_cis_p3 <- apply(boot_p3_results$t, 2, quantile, probs = c(0.025, 0.975))

boot_p3_summary <- data.frame(
  Effect = r2beta(p3, method = "nsj")$Effect,
  Boot_R2 = round(boot_r2_means_p3, 4),
  CI_Lower = round(boot_r2_cis_p3[1, ], 4),
  CI_Upper = round(boot_r2_cis_p3[2, ], 4)
)

print(boot_p3_summary)
```







