---
title: "Secondary Analysis"
author: "Christian Wollmann"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: true
    toc_depth: 2
    theme: united
---

0. Reading in required packages
```{r}
library(tidyverse) 
library(car)
library(DT)
library(dplyr)
library(tidyr)
library(lme4)
library(ggplot2)
library(influence.ME)
library(patchwork)
library(performance)
library(nortest)
library(parameters)
library(emmeans)
library(boot)
library(r2glmm)
library(clubSandwich)
library(knitr)
```

1. Model Specification

1.1 Reading in Data
```{r}
df_secondary <- read.csv("df_long.csv")


df_secondary$val_cat <- factor(df_secondary$val_cat, levels = c("neg", "neu", "pos")) 
df_secondary$gr <- factor(df_secondary$gr, levels = c("20Hz_online_exp", "20Hz_online_sham"))
```

1.2 Specification of lme4-models
```{r}
s1 <- lmer(val ~ gr * val_cat + (1|subj), data = df_secondary)

s2 <- lmer(val ~ gr * val_cat + age + sex + (1|subj), data = df_secondary)

s3 <- lmer(val ~ gr * val_cat + age + sex + rMT+ (1|subj), data = df_secondary)
```

1.3 Distribution of DV
```{r}
v <- ggplot(df_secondary, aes(x = val_cat, y = val, fill = gr)) +
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(width = 1), 
               alpha = 0.5, color = "black") +
  stat_summary(fun.data = mean_cl_normal, 
               geom = "errorbar", 
               position = position_dodge(width = 1), 
               width = 0.2, color = "black") +
  scale_fill_manual(values = c("20Hz_online_exp" = "#0072B2",
                               "20Hz_online_sham" = "#D55E00"),
               labels = c("experimental", "control"),
               name = "Group") +
  scale_x_discrete(labels = c("neg" = "negative", 
                              "neu" = "neutral", 
                              "pos" = "positive")) +
  labs(x = "", y = "", fill = "") +
  theme_minimal() +
  theme(legend.title = element_text(hjust = 0.5)) 
v
```

2. Verifying assumptions

2.1 Univariate outliers

visualization
```{r}
g2 <- ggplot(df_secondary, aes(x = "", y = val)) +  
  stat_boxplot(geom = "errorbar", width = 0.6, color = "black", alpha = 0.5, lwd = 0.3) +
  geom_boxplot(fill = "grey", color = "black", alpha = 0.5, lwd = 0.3, outlier.size = 2, outlier.shape = 8) +  
  geom_jitter(aes(color = gr), width = 0.3, height = 0, alpha = 0.8) +  
  scale_color_manual(
    values = c("20Hz_online_exp" = "#0072B2", 
               "20Hz_online_sham" = "#D55E00"),
    labels = c("experimental", "control"),
    name = "Group"
  ) +
  scale_y_continuous(limits = c(-200, 200)) +
  labs(x = NULL, y = NULL, title = NULL) +  
  theme_minimal() +
  theme(
    axis.text.y = element_text(size = 10),
    legend.title = element_text(size = 10, hjust = 0.5),
    legend.text = element_text(size = 9),
    panel.grid.minor = element_blank(), 
    panel.grid.major.x = element_blank(),
    axis.line = element_line(color = "black", linewidth = 0.5)
  )

g2
```

quantification
```{r}
Q1_val <- quantile(df_secondary$val, 0.25, na.rm = TRUE)
Q3_val <- quantile(df_secondary$val, 0.75, na.rm = TRUE)
IQR_val <- IQR(df_secondary$val, na.rm = TRUE)

lower_bound_val <- Q1_val - 1.5 * IQR_val
upper_bound_val <- Q3_val + 1.5 * IQR_val

outliers_val <- df_secondary %>%
  filter(val < lower_bound_val | val > upper_bound_val)

outliers_val
```

2.2 Multivariate Outliers: Cooks Distance

quantification
```{r}
#cd based on influential cases
inf_s1 <- influence(s1, obs = TRUE)
inf_s2 <- influence(s2, obs = TRUE)
inf_s3 <- influence(s3, obs = TRUE)

cd_s1 <- cooks.distance(inf_s1)
cd_s2 <- cooks.distance(inf_s2)
cd_s3 <- cooks.distance(inf_s3)

#find observations exceeding thresholds
critical_threshold <- 1
conservative_threshold <- 4 / nrow(df_secondary)

analyze_cooks_distance <- function(cd, model_name) {
  critical_points <- which(cd > critical_threshold)
  conservative_points <- which(cd > conservative_threshold)
  
  cat(paste("\n--- Cook's Distance Analysis for", model_name, "---\n"))
  
  if (length(critical_points) > 0) {
    cat("Indizes (CD > 1):\n")
    print(critical_points)
  } else {
    cat("Keine Punkte mit CD > 1 gefunden.\n")
  }
  
  if (length(conservative_points) > 0) {
    cat("Indizes (CD > 4/N):\n")
    print(conservative_points)
  } else {
    cat("Keine Punkte mit CD > 4/N gefunden.\n")
  }
}

analyze_cooks_distance(cd_s1, "s1")
analyze_cooks_distance(cd_s2, "s2")
analyze_cooks_distance(cd_s3, "s3"))

#mapping observations and subject
cd4n_s1 <- c(6, 36, 45)
cd4n_s2 <- c(4, 6, 36, 40, 45)
cd4n_s3 <- c(4, 6, 36, 45, 63)

subj_cd4n_s1 <- df_secondary$subj[cd4n_s1]
subj_cd4n_s2 <- df_secondary$subj[cd4n_s2]
subj_cd4n_s3 <- df_secondary$subj[cd4n_s3]

cat("\n--- Cook's Distance > 4/N: s1 ---\n")
cat("subj IDs:", subj_cd4n_s1, "\n")

cat("\n--- Cook's Distance > 4/N: s2 ---\n")
cat("subj IDs:", subj_cd4n_s2, "\n")

cat("\n--- Cook's Distance > 4/N: s3 ---\n")
cat("subj IDs:", subj_cd4n_s3, "\n")

```

visualization
```{r}
y_threshold_sec <- 4 / nrow(df_secondary)
y_limit_sec <- range(c(cd_s1, cd_s2, cd_s3, y_threshold_sec), na.rm = TRUE)

par(mfrow = c(1, 3), mai = c(0.5, 0.6, 0.3, 0.25), oma = c(3, 0, 0, 0))
#S1
plot(cd_s1, type = "h", main = "", 
     ylab = "", xlab = "", ylim = y_limit_sec, cex.lab = 1.2, col = "black")
abline(h = 1, col = "#0072B2", lty = 2)
abline(h = y_threshold_sec, col = "#CC79A7", lty = 2)
segments(x0 = cd4n_s1, y0 = 0, x1 = cd4n_s1, y1 = cd_s1[cd4n_s1], col = "red", lwd = 1)
#S2
plot(cd_s2, type = "h", main = "", 
     ylab = "", xlab = "", ylim = y_limit_sec, cex.lab = 1.2, col = "black")
abline(h = 1, col = "#0072B2", lty = 2)
abline(h = y_threshold_sec, col = "#CC79A7", lty = 2)
segments(x0 = cd4n_s2, y0 = 0, x1 = cd4n_s2, y1 = cd_s2[cd4n_s2], col = "red", lwd = 1)

#S3
plot(cd_s3, type = "h", main = "", 
     ylab = "", xlab = "", ylim = y_limit_sec, cex.lab = 1.2, col = "black")
abline(h = 1, col = "#0072B2", lty = 2)
abline(h = y_threshold_sec, col = "#CC79A7", lty = 2)
segments(x0 = cd4n_s3, y0 = 0, x1 = cd4n_s3, y1 = cd_s3[cd4n_s3], col = "red", lwd = 1)

mtext("Observation Index", side = 1, line = 1.5, outer = TRUE, cex = par("cex.lab"))

par(mfrow = c(1, 1))
```

looking at subject variable combinations in raw dataset
```{r}
unique_subjects <- unique(c(subj_cd4n_s1, subj_cd4n_s2, subj_cd4n_s3))

unique_subjects <- sort(unique_subjects)
unique_subjects
df_20hz %>% filter(VP_nr %in% c(207, 217, 220, 221))
```



2.3 Multicollinearity
quantification: VIF
```{r}
check_collinearity(s1)
check_collinearity(s2)
check_collinearity(s3)
```

2.4 Normal distribution of errors
calculate standardized residuals
```{r}
df_secondary$resid_s1 <- resid(s1)
df_secondary$resid_s2 <- resid(s2)
df_secondary$resid_s3 <- resid(s3)

df_secondary$stand_resid_s1 <- scale(df_secondary$resid_s1)[, 1]
df_secondary$stand_resid_s2 <- scale(df_secondary$resid_s2)[, 1]
df_secondary$stand_resid_s3 <- scale(df_secondary$resid_s3)[, 1]
```

preparing density distribution and KDE for plotting
```{r}
# KDE
s1_density <- data.frame(
  x = density(df_secondary$stand_resid_s1)$x,
  y = density(df_secondary$stand_resid_s1)$y,
  type = "Empirical Density"
)

s2_density <- data.frame(
  x = density(df_secondary$stand_resid_s2)$x,
  y = density(df_secondary$stand_resid_s2)$y,
  type = "Empirical Density"
)

s3_density <- data.frame(
  x = density(df_secondary$stand_resid_s3)$x,
  y = density(df_secondary$stand_resid_s3)$y,
  type = "Empirical Density"
)

#normal distribution
s1_normal <- data.frame(
  x = seq(min(df_secondary$stand_resid_s1), max(df_secondary$stand_resid_s1), length.out = 100),
  y = dnorm(seq(min(df_secondary$stand_resid_s1), max(df_secondary$stand_resid_s1), length.out = 100)),
  type = "Normal Distribution"
)

s2_normal <- data.frame(
  x = seq(min(df_secondary$stand_resid_s2), max(df_secondary$stand_resid_s2), length.out = 100),
  y = dnorm(seq(min(df_secondary$stand_resid_s2), max(df_secondary$stand_resid_s2), length.out = 100)),
  type = "Normal Distribution"
)

s3_normal <- data.frame(
  x = seq(min(df_secondary$stand_resid_s3), max(df_secondary$stand_resid_s3), length.out = 100),
  y = dnorm(seq(min(df_secondary$stand_resid_s3), max(df_secondary$stand_resid_s3), length.out = 100)),
  type = "Normal Distribution"
)
```

Visualization
```{r}
#S1
s1_lines <- rbind(s1_density, s1_normal)

s1_hist <- ggplot(df_secondary, aes(x = stand_resid_s1)) +
  geom_histogram(aes(y = ..density..), fill = "grey", color = "#000000", binwidth = 0.25) +
  geom_line(data = s1_lines, aes(x = x, y = y, color = type), linewidth = 1) +
  scale_color_manual(name = "Line Type", 
                     values = c("Empirical Density" = "#CC79A7", 
                                "Normal Distribution" = "#F0E442")) +
  labs(title = "", x = "", y = "") +
  theme_minimal() +
 theme(legend.title = element_text(hjust = 0.5)) 
s1_hist

df_secondary$theoretical_quantiles_s1 <- qqnorm(df_secondary$stand_resid_s1, plot.it = FALSE)$x

s1_qq <- ggplot(df_secondary, aes(x = theoretical_quantiles_s1, y = stand_resid_s1, color = gr)) +
  geom_jitter(width = 0.3, height = 0, size = 1.5, alpha = 0.7) +
  geom_abline(intercept = mean(df_secondary$stand_resid_s1), slope = sd(df_secondary$stand_resid_s1), color = "#CC79A7", linewidth = 1) +
  scale_color_manual(
    values = c("20Hz_online_exp" = "#0072B2", 
               "20Hz_online_sham" = "#D55E00"),
    labels = c("experimental", "control"),
    name = "Group"
  ) +
  labs(title = "", x = "", y = "") +
  theme_minimal() +
 theme(legend.title = element_text(hjust = 0.5)) 
s1_qq

#S2
s2_lines <- rbind(s2_density, s2_normal)

s2_hist <- ggplot(df_secondary, aes(x = stand_resid_s2)) +
  geom_histogram(aes(y = ..density..), fill = "grey", color = "#000000", binwidth = 0.25) +
  geom_line(data = s2_lines, aes(x = x, y = y, color = type), linewidth = 1) +
  scale_color_manual(name = "Line Type", 
                     values = c("Empirical Density" = "#CC79A7", 
                                "Normal Distribution" = "#F0E442")) +
  labs(title = "", x = "", y = "") +
  theme_minimal() +
 theme(legend.title = element_text(hjust = 0.5)) 
s2_hist

df_secondary$theoretical_quantiles_s2 <- qqnorm(df_secondary$stand_resid_s2, plot.it = FALSE)$x

s2_qq <- ggplot(df_secondary, aes(x = theoretical_quantiles_s2, y = stand_resid_s2, color = gr)) +
  geom_jitter(width = 0.3, height = 0, size = 1.5, alpha = 0.7) +
  geom_abline(intercept = mean(df_secondary$stand_resid_s2), slope = sd(df_secondary$stand_resid_s2), color = "#CC79A7", linewidth = 1) +
scale_color_manual(
    values = c("20Hz_online_exp" = "#0072B2", 
               "20Hz_online_sham" = "#D55E00"),
    labels = c("experimental", "control"),
    name = "Group"
  ) +  labs(title = "", x = "", y = "") +
  theme_minimal() +
 theme(legend.title = element_text(hjust = 0.5)) 
s2_qq

#S3
s3_lines <- rbind(s3_density, s3_normal)

s3_hist <- ggplot(df_secondary, aes(x = stand_resid_s3)) +
  geom_histogram(aes(y = ..density..), fill = "grey", color = "#000000", binwidth = 0.25) +
  geom_line(data = s3_lines, aes(x = x, y = y, color = type), linewidth = 1) +
  scale_color_manual(name = "Line Type", 
                     values = c("Empirical Density" = "#CC79A7", 
                                "Normal Distribution" = "#F0E442")) +
  labs(title = "", x = "", y = "") +
  theme_minimal() +
 theme(legend.title = element_text(hjust = 0.5)) 
s3_hist

df_secondary$theoretical_quantiles_s3 <- qqnorm(df_secondary$stand_resid_s3, plot.it = FALSE)$x

s3_qq <- ggplot(df_secondary, aes(x = theoretical_quantiles_s3, y = stand_resid_s3, color = gr)) +
  geom_jitter(width = 0.3, height = 0, size = 1.5, alpha = 0.7) +
  geom_abline(intercept = mean(df_secondary$stand_resid_s3), slope = sd(df_secondary$stand_resid_s3), color = "#CC79A7", linewidth = 1) +
scale_color_manual(
    values = c("20Hz_online_exp" = "#0072B2", 
               "20Hz_online_sham" = "#D55E00"),
    labels = c("experimental", "control"),
    name = "Group"
  ) +  labs(title = "", x = "", y = "") +
  theme_minimal() +
 theme(legend.title = element_text(hjust = 0.5)) 
s3_qq

```

quantification
```{r}
#S1
shapiro_residuals_s1 <- shapiro.test(df_secondary$resid_s1)
ad_residuals_s1 <- ad.test(df_secondary$resid_s1)

cat("\n#---------------------------------------#\n")
cat("## Model s1 - Normality Tests\n")
cat("\nShapiro-Wilk Test:\n")
print(shapiro_residuals_s1)
cat("\nAnderson-Darling Test:\n")
print(ad_residuals_s1)

#S2
shapiro_residuals_s2 <- shapiro.test(df_secondary$resid_s2)
ad_residuals_s2 <- ad.test(df_secondary$resid_s2)

cat("\n#---------------------------------------#\n")
cat("## Model s2 - Normality Tests\n")
cat("\nShapiro-Wilk Test:\n")
print(shapiro_residuals_s2)
cat("\nAnderson-Darling Test:\n")
print(ad_residuals_s2)

#S3
shapiro_residuals_s3 <- shapiro.test(df_secondary$resid_s3)
ad_residuals_s3 <- ad.test(df_secondary$resid_s3)

cat("\n#---------------------------------------#\n")
cat("## Model s3 - Normality Tests\n")
cat("\nShapiro-Wilk Test:\n")
print(shapiro_residuals_s3)
cat("\nAnderson-Darling Test:\n")
print(ad_residuals_s3)
```

2.5 Variance homogeneity
visualization
```{r}
#S1
df_secondary$fitted_s1 <- fitted(s1)
global_fit_s1 <- lm(resid(s1) ~ fitted(s1))

set.seed(123)
df_secondary$fitted_jit_s1 <- df_secondary$fitted_s1 + runif(nrow(df_secondary), -8, 8)

df_secondary$interval_s1 <- cut(
  df_secondary$fitted_s1,
  breaks = c(-200, -70, -30, 30, 70, 180),
  include.lowest = TRUE,
  right = FALSE
)

s1_var <- ggplot(df_secondary, aes(x = fitted_jit_s1, y = stand_resid_s1, color = gr)) +
  geom_segment(aes(x = fitted_jit_s1, xend = fitted_jit_s1, y = stand_resid_s1, yend = 0),
               color = "#009E73", linewidth = 0.1, alpha = 0.7) +
  geom_point(alpha = 0.8, size = 1.5) +
  geom_hline(aes(yintercept = 0, linetype = "No Deviation"), color = "black") +
  facet_wrap(~interval_s1, scales = "free_x") +
  scale_color_manual(
    values = c("20Hz_online_exp" = "#0072B2", "20Hz_online_sham" = "#D55E00"),
    labels = c("Experimental", "Sham"),
    name = "Group"
  ) +
  scale_linetype_manual(
    values = c("No Deviation" = "solid"),
    name = "Linetype"  
  ) +
  labs(title = "", x = "", y = "") +
  theme_minimal() +
 theme(legend.title = element_text(hjust = 0.5)) 
s1_var


#S2
df_secondary$fitted_s2 <- fitted(s2)
global_fit_s2 <- lm(resid(s2) ~ fitted(s2))

set.seed(123)
df_secondary$fitted_jit_s2 <- df_secondary$fitted_s2 + runif(nrow(df_secondary), -8, 8)

df_secondary$interval_s2 <- cut(
  df_secondary$fitted_s2,
  breaks = c(-200, -70, -30, 30, 70, 180),
  include.lowest = TRUE,
  right = FALSE
)

s2_var <- ggplot(df_secondary, aes(x = fitted_jit_s2, y = stand_resid_s2, color = gr)) +
  geom_segment(aes(x = fitted_jit_s2, xend = fitted_jit_s2, y = stand_resid_s2, yend = 0),
               color = "#009E73", linewidth = 0.1, alpha = 0.7) +
  geom_point(alpha = 0.8, size = 1.5) +
  geom_hline(aes(yintercept = 0, linetype = "No Deviation"), color = "black") +
  facet_wrap(~interval_s2, scales = "free_x") +
  scale_color_manual(
    values = c("20Hz_online_exp" = "#0072B2", "20Hz_online_sham" = "#D55E00"),
    labels = c("Experimental", "Sham"),
    name = "Group"
  ) +
  scale_linetype_manual(
    values = c("No Deviation" = "solid"),
    name = "Linetype"  
  ) +
  labs(title = "", x = "", y = "") +
   theme_minimal() +
  theme(legend.title = element_text(hjust = 0.5)) 
s2_var

#S3
df_secondary$fitted_s3 <- fitted(s3)
global_fit_s3 <- lm(resid(s2) ~ fitted(s3))

set.seed(123)
df_secondary$fitted_jit_s3 <- df_secondary$fitted_s3 + runif(nrow(df_secondary), -8, 8)

df_secondary$interval_s3 <- cut(
  df_secondary$fitted_s3,
  breaks = c(-200, -70, -30, 30, 70, 180),
  include.lowest = TRUE,
  right = FALSE
)

s3_var <- ggplot(df_secondary, aes(x = fitted_jit_s3, y = stand_resid_s3, color = gr)) +
  geom_segment(aes(x = fitted_jit_s3, xend = fitted_jit_s3, y = stand_resid_s3, yend = 0),
               color = "#009E73", linewidth = 0.1, alpha = 0.7) +
  geom_point(alpha = 0.8, size = 1.5) +
  geom_hline(aes(yintercept = 0, linetype = "No Deviation"), color = "black") +
  facet_wrap(~interval_s3, scales = "free_x") +
  scale_color_manual(
    values = c("20Hz_online_exp" = "#0072B2", "20Hz_online_sham" = "#D55E00"),
    labels = c("Experimental", "Sham"),
    name = "Group"
  ) +
  scale_linetype_manual(
    values = c("No Deviation" = "solid"),
    name = "Linetype"  
  ) +
  labs(title = "", x = "", y = "") +
  theme_minimal() +
  theme(legend.title = element_text(hjust = 0.5)) 
s3_var

```

quantification
```{r}
bp_s1 <- check_heteroscedasticity(s1)
bp_s2 <- check_heteroscedasticity(s2)
bp_s3 <- check_heteroscedasticity(s3)

print(bp_s1)
print(bp_s2)
print(bp_s3)
```

3. Inferential Analysis
3.1 Model Fit
```{r}
model_list_sec <- list(s1, s2, s3)
model_names_sec <- c("S1", "S2", "S3")

model_comparison_sec <- data.frame(
  Model = model_names_sec,
  AIC = sapply(model_list_sec, AIC),
  BIC = sapply(model_list_sec, BIC)
)

print(model_comparison_sec)

```

3.2 Model Results S1
linear mixed model results
```{r}
s1 <- lmer(val ~ gr * val_cat + (1|subj), data = df_secondary)
summary(s1)
model_parameters(s1, ci = 0.95)
```

robust results with CR2 confidence intervals
```{r}
compute_cr2_ci <- function(model, cluster_var, level = 0.95) {
  test <- coef_test(model, vcov = "CR2", cluster = cluster_var)
  
  alpha <- 1 - level
  t_crit <- qt(1 - alpha/2, df = test$df)
  
  ci_lower <- test$beta - t_crit * test$SE
  ci_upper <- test$beta + t_crit * test$SE
  
  result <- data.frame(
    Predictor = rownames(test),
    Estimate = round(test$beta, 4),
    SE_robust = round(test$SE, 4),
    df = round(test$df, 2),
    t = round(test$tstat, 3),
    p = round(test$p_Satt, 4),
    CI_lower = round(ci_lower, 4),
    CI_upper = round(ci_upper, 4)
  )
  
  return(result)
}
inference_s1_with_ci <- compute_cr2_ci(s1, df_secondary$subj)
kable(inference_s1_with_ci, caption = "Robust inference with 95% confidence intervals – Model s1")
```

bootstrapped effect sizes
```{r}
boot_r2_function <- function(model) {
  r2beta(model, method = "nsj")$Rsq
}

set.seed(123)
boot_s1_results <- bootMer(s1, FUN = boot_r2_function, nsim = 1000, use.u = TRUE, type = "parametric")

boot_r2_means_s1 <- apply(boot_s1_results$t, 2, mean)
boot_r2_cis_s1 <- apply(boot_s1_results$t, 2, quantile, probs = c(0.025, 0.975))

boot_s1_summary <- data.frame(
  Effect = r2beta(s1, method = "nsj")$Effect,
  Boot_R2 = round(boot_r2_means_s1, 4),
  CI_Lower = round(boot_r2_cis_s1[1, ], 4),
  CI_Upper = round(boot_r2_cis_s1[2, ], 4)
)

print(boot_s1_summary)
```


3.3 Model Results S2
linear mixed model results
```{r}
s2 <- lmer(val ~ gr * val_cat + age + sex + (1|subj), data = df_secondary)
model_parameters(s2, ci = 0.95)
summary(s2)
confint(s2, method = "profile")
```

robust results with CR2 confidence intervals
```{r}
inference_s2_with_ci <- compute_cr2_ci(s2, df_secondary$subj)

kable(inference_s2_with_ci, caption = "Robust inference with 95% confidence intervals – Model s2")
```

bootstrapped effect sizes
```{r}
set.seed(123)
boot_s2_results <- bootMer(s2, FUN = boot_r2_function, nsim = 1000, use.u = TRUE, type = "parametric")

boot_r2_means_s2 <- apply(boot_s2_results$t, 2, mean)
boot_r2_cis_s2 <- apply(boot_s2_results$t, 2, quantile, probs = c(0.025, 0.975))

boot_s2_summary <- data.frame(
  Effect = r2beta(s2, method = "nsj")$Effect,
  Boot_R2 = round(boot_r2_means_s2, 4),
  CI_Lower = round(boot_r2_cis_s2[1, ], 4),
  CI_Upper = round(boot_r2_cis_s2[2, ], 4)
)

print(boot_s2_summary)
```

Interaction plot with robust CR2 confidence intervals
```{r}
vcov_s2_cr2 <- vcovCR(s2, cluster = df_secondary$subj, type = "CR2")

emm_s2_robust <- emmeans(s2, ~ gr * val_cat, vcov. = vcov_s2_cr2)

emm_df_s2_robust <- as.data.frame(emm_s2_robust)

plot_s2_robust <- ggplot(emm_df_s2_robust, aes(x = val_cat, y = emmean, color = gr, group = gr)) +
  geom_line(linewidth = 1, position = position_dodge(0.3)) +
  geom_point(size = 3, position = position_dodge(0.3)) +
  geom_errorbar(
    aes(ymin = lower.CL, ymax = upper.CL),
    width = 0.15,
    position = position_dodge(0.3)
  ) +
  scale_x_discrete(labels = c("neg" = "Negative", "neu" = "Neutral", "pos" = "Positive")) +
  scale_color_manual(
    values = c("20Hz_online_exp" = "#0072B2", 
               "20Hz_online_sham" = "#D55E00"),
    labels = c("experimental", "control"),
    name = "Group"
  ) +
  labs(
    title = "",
    x = "",
    y = ""
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 11),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10)
  )

print(plot_s2_robust)
```

3.4 Model Results S3
linear mixed model results
```{r}
s3 <- lmer(val ~ gr * val_cat + age + sex + rMT + (1|subj), data = df_secondary)
summary(s3)
model_parameters(s3, ci = 0.95)
```

robust results with CR2 confidence intervals
```{r}
inference_s3_with_ci <- compute_cr2_ci(s3, df_secondary$subj)

kable(inference_s3_with_ci, caption = "Robust inference with 95% confidence intervals – Model s3")

```

bootstrapped effect sizes
```{r}
set.seed(123)
boot_s3_results <- bootMer(s3, FUN = boot_r2_function, nsim = 1000, use.u = TRUE, type = "parametric")

boot_r2_means_s3 <- apply(boot_s3_results$t, 2, mean)
boot_r2_cis_s3 <- apply(boot_s3_results$t, 2, quantile, probs = c(0.025, 0.975))

boot_s3_summary <- data.frame(
  Effect = r2beta(s3, method = "nsj")$Effect,
  Boot_R2 = round(boot_r2_means_s3, 4),
  CI_Lower = round(boot_r2_cis_s3[1, ], 4),
  CI_Upper = round(boot_r2_cis_s3[2, ], 4)
)

print(boot_s3_summary)
```
